Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | AI & digital&nbsp;humanities&nbsp;instructor </font>

### 2023-07-28 index.Rmd
news

@@

>>>>

* Juan Guerrero Montero, Andres Karjus, Kenny Smith, Richard A. Blythe. 2023. Reliable identification of selection mechanisms in language change | [preprint](https://arxiv.org/abs/2305.15914)

@@

* Mark Mets, Andres Karjus, Indrek Ibrus, Maximilian Schich. 2023. Automated stance detection in complex topics and small languages: the challenging case of immigration in polarizing news media | [preprint](https://arxiv.org/abs/2305.13047)
